SST_patterns

### 2020-01-20 SST_patterns.Rmd
Added correlation results by site and product comparing different distance pixels and the count of events within them

combined_freq_spread <- spread(Combined_frequency, distance, number_of_signals)

slope_calc <- function(df){
  df %>% 
    mutate(row_num = 1:n()) %>% 
    do(mod1 = lm(number_of_signals ~ row_num, data = .),
       mod2 = lm(distance ~ row_num, data = .),
       mod3 = lm(distance ~ number_of_signals, data = .),
       mod4 = cor(.$distance, .$number_of_signals, method = "pearson", use = "complete.obs")[1]) %>% 
    mutate(distance_slope = summary(mod1)$coeff[2],
           signal_slope = summary(mod2)$coeff[2],
           signal_distance_slope = summary(mod3)$coeff[2],
           signal_distance_r = mod4[1],
           signal_distance_r2 = glance(mod3)$adj.r.squared) %>%
    select(-mod1, -mod2, -mod3, -mod4) %>% 
    mutate_if(is.numeric, round, 2)
}

distance_corr <- Combined_frequency %>% 
  group_by(site, product) %>% 
  slope_calc()
```

>>>>

load("Data/Combined_frequency.RData")

combined_freq_spread <- pivot_wider(Combined_frequency, names_prefix = "dist_",
                                    names_from = distance, values_from = number_of_signals)

slope_calc <- function(df){
  df %>% 
    # mutate(row_num = 1:n()) %>% 
    # do(mod1 = lm(number_of_signals ~ row_num, data = .),
       # mod2 = lm(distance ~ row_num, data = .),
       # mod3 = lm(distance ~ number_of_signals, data = .),
       # mod4 = cor(.$distance, .$number_of_signals, method = "pearson", use = "complete.obs")[1]) %>% 
        # mutate(distance_slope = summary(mod1)$coeff[2],
        #    signal_slope = summary(mod2)$coeff[2],
        #    signal_distance_slope = summary(mod3)$coeff[2],
        #    signal_distance_r = mod4[1],
        #    signal_distance_r2 = glance(mod3)$adj.r.squared) %>%
        # select(-mod1, -mod2, -mod3, -mod4) %>% 
    do(mod1 = cor(.$dist_10, .$dist_30, method = "pearson", use = "complete.obs"),
       mod2 = cor(.$dist_10, .$dist_50, method = "pearson", use = "complete.obs")) %>%
    mutate(dist_10_vs_30_r = mod1[1],
           dist_10_vs_50_r = mod2[1]) %>% 
    # select(dist_10_vs_30_r, dist_10_vs_50_r) %>% 
    select(-mod1, -mod2) %>% 
    mutate_if(is.numeric, round, 2)
}

# test <- cor(combined_freq_spread$`10`, combined_freq_spread$`30`)

distance_corr <- combined_freq_spread %>% 
  group_by(site, product) %>% 
  slope_calc()
```
